Measuring contrast processing in the visual system using SSVEP

### 2024-04-20 review.qmd
Fixed plot output

plt.tight_layout()
plot.savefig('Figures/centresurround.pdf')

@@

axs[2].grid()
plt.tight_layout()
plot.savefig('Figures/linearsystem.pdf')

@@

axs[2].grid()
plt.tight_layout()
plot.savefig('Figures/transducer.pdf')

@@

axs[2].grid()
plt.tight_layout()
plot.savefig('Figures/twoinputs.pdf')

>>>>

plt.tight_layout()
plt.savefig('Figures/centresurround.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/linearsystem.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/transducer.pdf')

@@

axs[2].grid()
plt.tight_layout()
plt.savefig('Figures/twoinputs.pdf')
